---
title: "Prep data for Figure 4"
author: "Jacob T. Nearing"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(reshape2)
library(pheatmap)
library(plyr)

### Folders where final figures are written
### Make sure this is pointed to your home directory
display_items_out <- "/home/jacob/GitHub_Repos/Clean_Hackathon/Display_items/"

Data_set_names <- c(ArcticFireSoils="Soil - Fires",
                         ArcticFreshWater="Freshwater - Arctic",
                         ArcticTransects="Soil - Arctic",
                         art_scher="Human - RA",
                         asd_son= "Human - ASD",
                         BISCUIT= "Human - CD (1)",
                         Blueberry= "Soil - Blueberry",
                         Schubert="Human - C. diff (1)",
                         cdi_vincent="Human - C. diff (2)",
                         Chemerin="Mouse Facilities",
                         crc_baxter="Human - CC (1)",
                         crc_zeller="Human - CC (2)",
                         edd_singh="Human - Inf.",
                         Exercise="Mouse - Exercised",
                         glass_plastic_oberbeckmann="Marine - Plastic (4)",
                         GWMC_ASIA_NA="WWSR - Continents",
                         GWMC_HOT_COLD="WWSR - Temp.",
                         hiv_dinh="Human - HIV (1)",
                         hiv_lozupone="Human - HIV (2)",
                         Hiv_noguerajulian="Human - HIV (3)",
                         ibd_gevers="Human - CD (2)",
                         ibd_papa="Human - IBD",
                         Ji_WTP_DS="Freshwater - Treat.",
                         MALL="Human - ALL",
                         Goodrich="Human - OB (1)",
                         ob_ross="Human - OB (2)",
                         ob_turnbaugh="Human - OB (3)",
                         ob_zhu="Human - OB (4)",
                         ###"ob_zupancic",
                         Office="Built - Office",
                         par_scheperjans="Human - Par.",
                         sed_plastic_hoellein="Marine - Plastic (2)",
                         sed_plastic_rosato="Marine - Plastic (5)",
                         seston_plastic_mccormick="River - Plastic",
                         sw_plastic_frere="Marine - Plastic (1)",
                         Sw_sed_detender="Marine - Sediment",
                          t1d_alkanani="Human - T1D (1)",
                         t1d_mejialeon="Human - T1D (2)",
                         wood_plastic_kesy="Marine - Plastic (3)")

tool_names <- c(aldex2="ALDEx2", ancom="ANCOM-II", corncob="corncob", deseq2="DESeq2", edger="edgeR", lefse="LEfSe", 
                limma_voom_TMM="limma voom (TMM)", limma_voom_TMMwsp="limma voom (TMMwsp)", maaslin2="MaAsLin2",
                maaslin2rare="MaAsLin2 (rare)", metagenomeSeq="metagenomeSeq", ttestrare="t-test (rare)", 
                wilcoxonclr="Wilcoxon (CLR)", wilcoxonrare="Wilcoxon (rare)")
```

# Load in data

## Load in data functions
```{r}
read_table_and_check_line_count <- function(filepath, ...) {
  # Function to read in table and to check whether the row count equals the expected line count of the file.
  
  exp_count <- as.numeric(sub(pattern = " .*$", "", system(command = paste("wc -l", filepath, sep=" "), intern = TRUE)))
  
  df <- read.table(filepath, ...)
  
  if(length(grep("^V", colnames(df))) != ncol(df)) {
    exp_count <- exp_count - 1
  }
  
  if(exp_count != nrow(df)) {
    stop(paste("Expected ", as.character(exp_count), " lines, but found ", as.character(nrow(df))))
  } else {
    return(df) 
  }
}


read_hackathon_results <- function(study) {
  
  da_tool_filepath <- list()
  da_tool_filepath[["aldex2"]] <- paste(study, "Aldex_out/Aldex_res.tsv", sep = "/")
  da_tool_filepath[["ancom"]] <- paste(study, "ANCOM_out/Ancom_res.tsv", sep = "/")
  da_tool_filepath[["corncob"]] <- paste(study, "Corncob_out/Corncob_results.tsv", sep = "/")
  da_tool_filepath[["deseq2"]] <- paste(study, "Deseq2_out/Deseq2_results.tsv", sep = "/")
  da_tool_filepath[["edger"]] <- paste(study, "edgeR_out/edgeR_res.tsv", sep = "/")
  da_tool_filepath[["lefse"]] <- paste(study,"Lefse_out/Lefse_results.tsv", sep = "/")
  da_tool_filepath[["maaslin2"]] <- paste(study, "Maaslin2_out/all_results.tsv", sep = "/")
  da_tool_filepath[["maaslin2rare"]] <- paste(study, "Maaslin2_rare_out/all_results.tsv", sep = "/")
  da_tool_filepath[["metagenomeSeq"]] <- paste(study, "metagenomeSeq_out/mgSeq_res.tsv", sep = "/")
  da_tool_filepath[["ttestrare"]] <- paste(study, "t_test_rare_out/t_test_res.tsv", sep = "/")
  da_tool_filepath[["wilcoxonclr"]] <- paste(study, "Wilcoxon_CLR_out/Wil_CLR_results.tsv", sep = "/")
  da_tool_filepath[["wilcoxonrare"]] <- paste(study, "Wilcoxon_rare_out/Wil_rare_results.tsv", sep = "/")
  da_tool_filepath[["limma_voom_TMM"]] <- paste(study, "limma_voom_tmm_out/limma_voom_tmm_res.tsv", sep="/")
  da_tool_filepath[["limma_voom_TMMwsp"]] <- paste(study, "Limma_voom_TMMwsp/limma_voom_tmmwsp_res.tsv", sep="/")
  
  adjP_colname <- list()
  adjP_colname[["aldex2"]] <- "wi.eBH"
  adjP_colname[["ancom"]] <- "detected_0.9"
  adjP_colname[["corncob"]] <- "x"
  adjP_colname[["deseq2"]] <- "padj"
  adjP_colname[["edger"]] <- "FDR"
  adjP_colname[["lefse"]] <- "V5"
  adjP_colname[["maaslin2"]] <- "qval"
  adjP_colname[["maaslin2rare"]] <- "qval"
  adjP_colname[["metagenomeSeq"]] <- "adjPvalues"
  adjP_colname[["ttestrare"]] <- "x"
  adjP_colname[["wilcoxonclr"]] <- "x"
  adjP_colname[["wilcoxonrare"]] <- "x"
  adjP_colname[["limma_voom_TMM"]] <- "adj.P.Val"
  adjP_colname[["limma_voom_TMMwsp"]] <- "adj.P.Val"
  # Read in results files and run sanity check that results files have expected number of lines
  da_tool_results <- list()
  
  missing_tools <- c()
  
  for(da_tool in names(da_tool_filepath)) {
    
    if(! (file.exists(da_tool_filepath[[da_tool]]))) {
       missing_tools <- c(missing_tools, da_tool)
       message(paste("File ", da_tool_filepath[[da_tool]], " not found. Skipping.", sep=""))
       next
    }
    
    if(da_tool %in% c("ancom", "maaslin2", "maaslin2rare")) {
      da_tool_results[[da_tool]] <- read_table_and_check_line_count(da_tool_filepath[[da_tool]], sep="\t", row.names=2, header=TRUE)
    } else if(da_tool == "lefse") {
      da_tool_results[[da_tool]] <- read_table_and_check_line_count(da_tool_filepath[[da_tool]], sep="\t", row.names=1, header=FALSE, stringsAsFactors=FALSE)
      rownames(da_tool_results[[da_tool]]) <- gsub("^f_", "", rownames(da_tool_results[[da_tool]]))
    } else {
      da_tool_results[[da_tool]] <- read_table_and_check_line_count(da_tool_filepath[[da_tool]], sep="\t", row.names=1, header=TRUE)
    }
  }
  
  # Combine corrected P-values into same table.
  all_rows <- c()
  
   for(da_tool in names(adjP_colname)) {
     all_rows <- c(all_rows, rownames(da_tool_results[[da_tool]]))
   }
  all_rows <- all_rows[-which(duplicated(all_rows))]

  adjP_table <- data.frame(matrix(NA, ncol=length(names(da_tool_results)), nrow=length(all_rows)))
  colnames(adjP_table) <- names(da_tool_results)
  rownames(adjP_table) <- all_rows
  
  for(da_tool in colnames(adjP_table)) {
 
    if(da_tool %in% missing_tools) {
       next
    }
    
    if(da_tool == "lefse") {
     
        tmp_lefse <- da_tool_results[[da_tool]][, adjP_colname[[da_tool]]]
        tmp_lefse[which(tmp_lefse == "-")] <- NA
        adjP_table[rownames(da_tool_results[[da_tool]]), da_tool] <- as.numeric(tmp_lefse)

        lefse_tested_asvs <- rownames(da_tool_results$wilcoxonrare)[which(! is.na(da_tool_results$wilcoxonrare))]
        lefse_NA_asvs <- rownames(da_tool_results$lefse)[which(is.na(tmp_lefse))]
  
        adjP_table[lefse_NA_asvs[which(lefse_NA_asvs %in% lefse_tested_asvs)], da_tool] <- 1
        
    } else if(da_tool == "ancom") {
      
      sig_ancom_hits <- which(da_tool_results[[da_tool]][, adjP_colname[[da_tool]]])
      ancom_results <- rep(1, length(da_tool_results[[da_tool]][, adjP_colname[[da_tool]]]))
      ancom_results[sig_ancom_hits] <- 0
      adjP_table[rownames(da_tool_results[[da_tool]]), da_tool] <- ancom_results
    
    } else if(da_tool %in% c("wilcoxonclr", "wilcoxonrare", "ttestrare")) {
      
      # Need to perform FDR-correction on these outputs.
      adjP_table[rownames(da_tool_results[[da_tool]]), da_tool] <- p.adjust(da_tool_results[[da_tool]][, adjP_colname[[da_tool]]], "fdr")
    
    } else {
      adjP_table[rownames(da_tool_results[[da_tool]]), da_tool] <- da_tool_results[[da_tool]][, adjP_colname[[da_tool]]]
    }
  }

  return(list(raw_tables=da_tool_results,
              adjP_table=adjP_table))
  
}

```

## Data loading

### Filtered

#### Office
```{r}
Filtered_FD_data <- list()

setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13//Hackathon/Studies/Office/False_Discovery_Testing/results_filt/")


Office_filt_results <- lapply(c(1:100), read_hackathon_results)

#get adj_p for each table run

Office_filt_p_tabs <- list()
for(i in 1:100){
 Office_filt_p_tabs[[i]] <- Office_filt_results[[i]]$adjP_table
  
}


Filtered_FD_data[["Office"]] <- Office_filt_p_tabs


```

#### ArcticFreshWaters
```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/ArcticFreshwaters/False_Discovery_Testing/results_filt/")

Arctic_results_filt <- lapply(c(1:100), read_hackathon_results)

Arctic_filt_p_tabs <- list()

for(i in 1:100){
  
  Arctic_filt_p_tabs[[i]] <- Arctic_results_filt[[i]]$adjP_table
}


Filtered_FD_data[["ArcticFreshWaters"]] <- Arctic_filt_p_tabs

```

#### Blueberry
```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/Blueberry/False_Discovery_Testing/results_filt/")


Blueb_filt_results <- lapply(c(1:100), read_hackathon_results)

Blueb_filt_p_tabs <- list()

for(i in 1:100){
  
  Blueb_filt_p_tabs[[i]] <- Blueb_filt_results[[i]]$adjP_table
}


Filtered_FD_data[["Blueberry"]] <- Blueb_filt_p_tabs
```

#### Goodrich
```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/ob_goodrich/False_Discovery_Testing/results_filt/")

goodrich_filt_results <- lapply(c(1:100), read_hackathon_results)

goodrich_filt_p_tabs <- list()

for(i in 1:100){
  
  goodrich_filt_p_tabs[[i]] <- goodrich_filt_results[[i]]$adjP_table
  
}

Filtered_FD_data[["ob_goodrich"]] <- goodrich_filt_p_tabs
```

#### hiv_noguerajulian

```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/hiv_noguerajulian/False_Discovery_Testing/results_filt/")

hiv_nog_filt_results <- lapply(c(1:100), read_hackathon_results)

hiv_nog_filt_p_tabs <- list()

for(i in 1:100){
  
  hiv_nog_filt_p_tabs[[i]] <- hiv_nog_filt_results[[i]]$adjP_table
  
}

Filtered_FD_data[["hiv_noguerajulian"]] <- hiv_nog_filt_p_tabs
```

#### Ji_WTP_DS
```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/Ji_WTP_DS/False_Discovery_Testing/results_filt/")

JI_WTP_filt_results <- lapply(c(1:100), read_hackathon_results)

JI_WTP_filt_p_tabs <- list()

for(i in 1:100){
  
  JI_WTP_filt_p_tabs[[i]] <- JI_WTP_filt_results[[i]]$adjP_table
  
}

Filtered_FD_data[["Ji_WTP_DS"]] <- JI_WTP_filt_p_tabs
```

#### Schubert
```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/cdi_schubert/False_Discovery_Testing/results_filt/")

schubert_filt_results <- lapply(c(1:100), read_hackathon_results)

schubert_filt_p_tabs <- list()

for(i in 1:100){
  
  schubert_filt_p_tabs[[i]] <- schubert_filt_results[[i]]$adjP_table
  
}

Filtered_FD_data[["cdi_schubert"]] <- schubert_filt_p_tabs
```

#### sw_sed_detender
```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/sw_sed_detender/False_Discovery_Testing/results_filt/")

sw_sed_filt_results <- lapply(c(1:100), read_hackathon_results)

sw_sed_filt_p_tabs <- list()

for(i in 1:100){
  
  sw_sed_filt_p_tabs[[i]] <- sw_sed_filt_results[[i]]$adjP_table
}
Filtered_FD_data[["sw_sed_detender"]] <- sw_sed_filt_p_tabs
```

#### Save list
```{r}
saveRDS(Filtered_FD_data, "/home/jacob/GitHub_Repos/Hackathon_testing/Data/FD_data_filt_21_09_17.RDS")
```

### Unfiltered
```{r}
Unfiltered_FD_data <- list()
Unfiltered_FD_data_ext <- list()
```

#### ArcticFreshWaters

```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/ArcticFreshwaters/False_Discovery_Testing/results_nonfilt/")

arcticfresh_nonfilt <- lapply(c(1:10), read_hackathon_results)


arcticfresh_nonfilt_p_tabs <- list()

for(i in 1:10){
  
  arcticfresh_nonfilt_p_tabs[[i]] <- arcticfresh_nonfilt[[i]]$adjP_table
  
}

Unfiltered_FD_data[["ArcticFreshWaters"]] <- arcticfresh_nonfilt_p_tabs



setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/ArcticFreshwaters/False_Discovery_Testing/results_nonfilt_ext/")


arcticfresh_nonfilt_ext <- lapply(c(1:90), read_hackathon_results)

arcticfresh_nonfilt_p_tabs_ext <- list()

for(i in 1:90){
  
    arcticfresh_nonfilt_p_tabs_ext[[i]] <- arcticfresh_nonfilt_ext[[i]]$adjP_table
  
}


Unfiltered_FD_data_ext[["ArcticFreshWaters"]] <- arcticfresh_nonfilt_p_tabs_ext

```

#### Blueberry
```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/Blueberry/False_Discovery_Testing/results_nonfilt/")

Blueberry_nonfilt <- lapply(c(1:10), read_hackathon_results)

Blueberry_nonfilt_p_tabs <- list()

for(i in 1:10){
  
  Blueberry_nonfilt_p_tabs[[i]] <- Blueberry_nonfilt[[i]]$adjP_table
  
}

Unfiltered_FD_data[["Blueberry"]] <- Blueberry_nonfilt_p_tabs


setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/Blueberry/False_Discovery_Testing/results_nonfilt_ext/")

Blueberry_nonfilt_ext <- lapply(c(1:90), read_hackathon_results)

Blueberry_nonfilt_p_tabs_ext <- list()

for(i in 1:90){
  
  Blueberry_nonfilt_p_tabs_ext[[i]] <- Blueberry_nonfilt_ext[[i]]$adjP_table
  
}

Unfiltered_FD_data_ext[["Blueberry"]] <- Blueberry_nonfilt_p_tabs_ext

```

#### ob_goodrich
```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/ob_goodrich/False_Discovery_Testing/results_nonfilt/")

goodrich_nonfilt <- lapply(c(1:10), read_hackathon_results)

goodrich_nonfilt_p_tabs <- list()


for(i in 1:10){
  
  goodrich_nonfilt_p_tabs[[i]] <- goodrich_nonfilt[[i]]$adjP_table
  
}

Unfiltered_FD_data[["ob_goodrich"]] <- goodrich_nonfilt_p_tabs

setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/ob_goodrich/False_Discovery_Testing/results_nonfilt_ext/")

goodrich_nonfilt_ext <- lapply(c(1:90), read_hackathon_results)



goodrich_nonfilt_p_tabs_ext <- list()

for(i in 1:90){
  
    goodrich_nonfilt_p_tabs_ext[[i]] <- goodrich_nonfilt_ext[[i]]$adjP_table
  
}

Unfiltered_FD_data_ext[["ob_goodrich"]] <- goodrich_nonfilt_p_tabs_ext



```

#### hiv_noguerajulian

Need to run Ancom and Cornco on this dataset

```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/hiv_noguerajulian/False_Discovery_Testing/results_nonfilt/")

hiv_nog_nonfilt <- lapply(c(1:10), read_hackathon_results)

hiv_nog_nonfilt_p_tabs <- list()


for(i in 1:10){
  
  hiv_nog_nonfilt_p_tabs[[i]] <- hiv_nog_nonfilt[[i]]$adjP_table
}

Unfiltered_FD_data[["hiv_noguerajulian"]] <- hiv_nog_nonfilt_p_tabs

setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/hiv_noguerajulian/False_Discovery_Testing/results_nonfilt_ext/")


hiv_nog_nonfilt_ext <- lapply(c(1:90), read_hackathon_results)
#ancom and corncob need to be run on this dataset...

hiv_nog_nonfilt_p_tabs_ext <- list()



for(i in 1:90){
  
  hiv_nog_nonfilt_p_tabs_ext[[i]] <- hiv_nog_nonfilt_ext[[i]]$adjP_table
}

Unfiltered_FD_data_ext[["hiv_noguerajulian"]] <- hiv_nog_nonfilt_p_tabs_ext

```

#### Ji_WTP_DS

Need to run all three

```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/Ji_WTP_DS/False_Discovery_Testing/results_nonfilt/")

JI_WTP_nonfilt <- lapply(c(1:10), read_hackathon_results)

JI_WTP_nonfilt_p_tabs <- list()

for(i in 1:10){
  
  JI_WTP_nonfilt_p_tabs[[i]] <- JI_WTP_nonfilt[[i]]$adjP_table
  
}

Unfiltered_FD_data[["Ji_WTP_DS"]] <- JI_WTP_nonfilt_p_tabs


setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/Ji_WTP_DS/False_Discovery_Testing/results_nonfilt_ext/")

JI_WTP_nonfilt_ext <- lapply(c(1:90), read_hackathon_results)


JI_WTP_nonfilt_p_tabs_ext <- list()

for(i in 1:90){
  
  JI_WTP_nonfilt_p_tabs_ext[[i]] <- JI_WTP_nonfilt_ext[[i]]$adjP_table
  
}

Unfiltered_FD_data_ext[["Ji_WTP_DS"]] <- JI_WTP_nonfilt_p_tabs_ext

```

#### Office


Need to run all three


```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/Office/False_Discovery_Testing/results_nonfilt/")

## have to skip 5 as aldex2 didn't finish due to memory issues with other stuff being run..
Office_nonfilt <- lapply(c(1:10), read_hackathon_results)

Office_nonfilt_p_tabs <- list()

for(i in 1:10){
  message(i)
  Office_nonfilt_p_tabs[[i]] <- Office_nonfilt[[i]]$adjP_table
}


Unfiltered_FD_data[["Office"]] <- Office_nonfilt_p_tabs


setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/Office/False_Discovery_Testing/results_nonfilt_ext/")

Office_nonfilt_ext <- lapply(c(1:90), read_hackathon_results)

Office_nonfilt_p_tabs_ext <- list()

for(i in 1:90){
  Office_nonfilt_p_tabs_ext[[i]] <- Office_nonfilt_ext[[i]]$adjP_table
}


Unfiltered_FD_data_ext[["Office"]] <- Office_nonfilt_p_tabs_ext


```

#### cdi_schubert

Need to run all three


```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/cdi_schubert/False_Discovery_Testing/results_nonfilt/")

schubert_nonfilt <- lapply(c(1:10), read_hackathon_results)

schubert_nonfilt_p_tabs <- list()

for(i in 1:10){
  
  schubert_nonfilt_p_tabs[[i]] <- schubert_nonfilt[[i]]$adjP_table
    
}

Unfiltered_FD_data[["cdi_schubert"]] <- schubert_nonfilt_p_tabs

setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/cdi_schubert/False_Discovery_Testing/results_nonfilt_ext/")


schubert_nonfilt_ext <- lapply(c(1:90), read_hackathon_results)


schubert_nonfilt_p_tabs_ext <- list()

for(i in 1:90){
  
  schubert_nonfilt_p_tabs_ext[[i]] <- schubert_nonfilt_ext[[i]]$adjP_table
    
}


Unfiltered_FD_data_ext[["cdi_schubert"]] <- schubert_nonfilt_p_tabs_ext
```

#### sw_sed_detender

Need to run all three


```{r}
setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/sw_sed_detender/False_Discovery_Testing/results_nonfilt/")

sw_sed_nonfilt <- lapply(c(1:10), read_hackathon_results)

sw_sed_nonfilt_p_tabs <- list()

for(i in 1:10){
  
  sw_sed_nonfilt_p_tabs[[i]] <- sw_sed_nonfilt[[i]]$adjP_table
  
}

Unfiltered_FD_data[["sw_sed_detender"]] <- sw_sed_nonfilt_p_tabs



setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/sw_sed_detender/False_Discovery_Testing/results_nonfilt_ext/")


sw_sed_nonfilt_ext <- lapply(c(1:90), read_hackathon_results)


sw_sed_nonfilt_p_tabs_ext <- list()

for(i in 1:90){
  
  sw_sed_nonfilt_p_tabs_ext[[i]] <- sw_sed_nonfilt_ext[[i]]$adjP_table
  
}

Unfiltered_FD_data_ext[["sw_sed_detender"]] <- sw_sed_nonfilt_p_tabs_ext
```

#### Save data
```{r}
saveRDS(Unfiltered_FD_data, "/home/jacob/GitHub_Repos/Hackathon_testing/Data/FD_data_unfilt_21_04_08.RDS")
saveRDS(Unfiltered_FD_data_ext, "/home/jacob/GitHub_Repos/Hackathon_testing/Data/FD_data_ext_21_04_08.RDS")
```
