---
title: "Discriminatory Analysis"
author: "Jacob T. Nearing"
date: "7/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/")


display_items_out <- "/home/jacob/GitHub_Repos/Clean_Hackathon/Display_items/"

library(ROCR)
library(pheatmap)
library(foreach)
library(doParallel)
library(ggplot2)
library(reshape2)
library(cowplot)

library(RColorBrewer)
library(ggbeeswarm)
n <- 38
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))

Data_set_names <- c(ArcticFireSoils="Soil - Fires",
                         ArcticFreshwaters="Freshwater - Arctic",
                         ArcticTransects="Soil - Arctic",
                         art_scher="Human - RA",
                         asd_son= "Human - ASD",
                         BISCUIT= "Human - CD (1)",
                         Blueberry= "Soil - Blueberry",
                         cdi_schubert="Human - C. diff (1)",
                         cdi_vincent="Human - C. diff (2)",
                         Chemerin="Mouse Facilities",
                         crc_baxter="Human - CC (1)",
                         crc_zeller="Human - CC (2)",
                         edd_singh="Human - Inf.",
                         Exercise="Mouse - Exercised",
                         glass_plastic_oberbeckmann="Marine - Plastic (4)",
                         GWMC_ASIA_NA="WWSR - Continents",
                         GWMC_HOT_COLD="WWSR - Temp.",
                         hiv_dinh="Human - HIV (1)",
                         hiv_lozupone="Human - HIV (2)",
                         hiv_noguerajulian="Human - HIV (3)",
                         ibd_gevers="Human - CD (2)",
                         ibd_papa="Human - IBD",
                         Ji_WTP_DS="Freshwater - Treat.",
                         MALL="Human - ALL",
                         ob_goodrich="Human - OB (1)",
                         ob_ross="Human - OB (2)",
                         ob_turnbaugh="Human - OB (3)",
                         ob_zhu="Human - OB (4)",
                         ###"ob_zupancic",
                         Office="Built - Office",
                         par_scheperjans="Human - Par.",
                         sed_plastic_hoellein="Marine - Plastic (2)",
                         sed_plastic_rosato="Marine - Plastic (5)",
                         seston_plastic_mccormick="River - Plastic",
                         sw_plastic_frere="Marine - Plastic (1)",
                         sw_sed_detender="Marine - Sediment",
                          t1d_alkanani="Human - T1D (1)",
                         t1d_mejialeon="Human - T1D (2)",
                         wood_plastic_kesy="Marine - Plastic (3)")

tool_names <- c(aldex2="ALDEx2", ancom="ANCOM-II", corncob="corncob", deseq2="DESeq2", edger="edgeR", lefse="LEfSe", 
                limma_voom_TMM="limma voom (TMM)", limma_voom_TMMwsp="limma voom (TMMwsp)", maaslin2="MaAsLin2",
                maaslin2rare="MaAsLin2 (rare)", metagenomeSeq="metagenomeSeq", ttestrare="t-test (rare)", 
                wilcoxonclr="Wilcoxon (CLR)", wilcoxonrare="Wilcoxon (rare)")


## function to read in all the metadata files
read_metadata <- function(study_list){
  ret_meta <- list()
  
  for(i in 1:length(study_list)){
    
    meta_file <- list.files(study_list[i], pattern="*_meta*")
    meta_file_name <- paste(study_list[i], meta_file, sep="/")
    message(meta_file_name)
    ret_meta[[study_list[i]]] <- read.table(meta_file_name, header=T, sep="\t", comment.char="", quote="", check.names = F, row.names = 1)
  }
  return(ret_meta)
}
```

## load in data

```{r}
filt_results <- readRDS("/home/jacob/GitHub_Repos/Hackathon_testing/Data/Filt_results_21_04_07.RDS")
unfilt_results <- readRDS("/home/jacob/GitHub_Repos/Hackathon_testing/Data/Unfilt_results_21_04_07.RDS")

unfilt_study_tab  <- readRDS("/home/jacob/GitHub_Repos/Hackathon_testing/Data/unfilt_study_tab_21_04_07.RDS")
filt_study_tab <- readRDS("/home/jacob/GitHub_Repos/Hackathon_testing/Data/filt_study_tab_21_04_07.RDS")

## load in data classes
hackathon_study_ids <- c("ArcticFireSoils",
                         "ArcticFreshwaters",
                         "ArcticTransects",
                         "art_scher",
                         "asd_son",
                         "BISCUIT",
                         "Blueberry",
                         "cdi_schubert",
                         "cdi_vincent",
                         "Chemerin",
                         "crc_baxter",
                         "crc_zeller",
                         "edd_singh",
                         "Exercise",
                         "glass_plastic_oberbeckmann",
                         "GWMC_ASIA_NA",
                         "GWMC_HOT_COLD",
                         "hiv_dinh",
                         "hiv_lozupone",
                         "hiv_noguerajulian",
                         "ibd_gevers",
                         "ibd_papa",
                         "Ji_WTP_DS",
                         "MALL",
                         "ob_goodrich",
                         "ob_ross",
                         "ob_turnbaugh",
                         "ob_zhu",
                         ###"ob_zupancic",
                         "Office",
                         "par_scheperjans",
                         "sed_plastic_hoellein",
                         "sed_plastic_rosato",
                         "seston_plastic_mccormick",
                         "sw_plastic_frere",
                         "sw_sed_detender",
                          "t1d_alkanani",
                         "t1d_mejialeon",
                         "wood_plastic_kesy")


metadata <- read_metadata(hackathon_study_ids)
```

# Data generation
## Function

```{r}
## first function takes in p-value table and the corresponding table
get_discrim <- function(p_tab, study_tab, meta, norm_type="R.A"){
  
  #set all significant hits to value of 2
  p_tab_fix <- p_tab
  
  ## 2 represents a significant hit
  p_tab_fix[p_tab_fix < 0.05 ] <- 2
  
  ## anything that is not 2 (sig hit) we set as 0 (i.e. negative result)
  p_tab_fix[p_tab_fix != 2 ] <- 0
  
  # anything that was 2 (sig hit) we set as 1 (i.e. positive result)
  p_tab_fix[p_tab_fix == 2] <- 1
  
  ## value of 0 is non-sig, value of 1 is sig
  
  ## this list will contain lists for tool and the resulting AUROC
  disc_res <- list()
  ### we have to go through each column of p_tab
  for(i in 1:length(colnames(p_tab_fix))){
    
    ## for this tool we need to get the ID of all sig hits
    sig_feats <- rownames(p_tab_fix)[which(p_tab_fix[, i] == 1)]

    #get tool name that we are testing
    tool <- colnames(p_tab_fix)[i]
    ## okay for each sig feat
    
    #check the type of normalization that we want to use
    if(norm_type=="R.A"){
          #normalize the table to relative abundances (sum columns and than divide values by that sum (TSS))
          study_tab_norm <- sweep(study_tab, 2, colSums(study_tab), '/')
    }else if(norm_type=="CLR"){
      study_tab_norm <- data.frame(apply(study_tab + 1, 2, function(x) {log(x) - mean (log(x))} ), check.names = F)
    }else{
      message("Please pick a normalization method")
      stop()
    }
    
    #okay now we need to take each sig feat and make a prediction
    # vector that contains auroc_res for that tool on the dataset of interest
    auroc_res <- vector()
    
    #make sure we only include samples that are in the metadata that is provided.
    if(!identical(colnames(study_tab_norm), rownames(meta))){
      rows_to_keep <- intersect(colnames(study_tab_norm), rownames(meta))
      meta <- meta[rows_to_keep,,drop=F]
      study_tab_norm <- study_tab_norm[,rows_to_keep]
    }
    #if there are no sig hits for that tool set the value for that tool to NULL
    if(length(sig_feats)==0){
      message("No hits for this tool")
      disc_res[[tool]] <- NULL
    }
    else{
      #Go through each sig hit that was identified by the tool
      for(i in 1:length(sig_feats)){
        #get the abundance data for that feature
        test_data <- as.numeric(study_tab_norm[sig_feats[i],])
        ### one issue is that the prediction assumes that a higher number is indicative of the second class
        ### this is obviously not what we want in this analysis as the microbe could be up or down in either class
        ### we will need to fix this when calculating the auroc performance
        ### as such we will subtract the result from 0.5 and take the abs and than add 0.5 back. 
        ### this will give us classification performance in either direction.
        test_pred <- prediction(predictions = test_data, labels = meta[,1])
        test_perf <- performance(test_pred, measure="auc")
        test_result <- abs(0.5 - as.numeric(test_perf@y.values[1])) + 0.5
        
        auroc_res <- c(auroc_res, test_result)
      
      }
    }
    #set the names for each result to the correct ASV name
    names(auroc_res) <- sig_feats
    #Add the result to the list that contains the result for that tool
    disc_res[[tool]] <- auroc_res
    
  }
  return(disc_res)
}


#this function will calculate the AUROC of all features in a dataset depending on the normalization type.
get_AUROC_all_feats <- function(study_tab, meta, norm_type="R.A"){
   
    ## Normalize table
   if(norm_type=="R.A"){
          study_tab_norm <- sweep(study_tab, 2, colSums(study_tab), '/')
    }else if(norm_type=="CLR"){
      study_tab_norm <- data.frame(apply(study_tab + 1, 2, function(x) {log(x) - mean (log(x))} ), check.names = F)
    }else{
      message("Please pick a normalization method")
      stop()
    }
  
    ## make sure metadata and study table have same samples
    if(!identical(colnames(study_tab_norm), rownames(meta))){
      rows_to_keep <- intersect(colnames(study_tab_norm), rownames(meta))
      meta <- meta[rows_to_keep,,drop=F]
      study_tab_norm <- study_tab_norm[,rows_to_keep]
    }
    auroc_res <- vector()
    for(i in 1:length(rownames(study_tab_norm))){
      test_data <- as.numeric(study_tab_norm[i,])
      ### one issue is that the prediction assumes that a higher number is indicative of the second class
      ### this is obviously not what we want in this analysis as the microbe could be up or down in either class
      ### we will need to fix this when calculating the auroc performance
      ### as such we will subtract the result from 0.5 and take the abs and than add 0.5 back. 
      ### this will give us classification performance in either direction.
      test_pred <- ROCR::prediction(predictions = test_data, labels = meta[,1])
      test_perf <- ROCR::performance(test_pred, measure="auc")
      test_result <- abs(0.5 - as.numeric(test_perf@y.values[1])) + 0.5
      auroc_res <- c(auroc_res, test_result)
      
    }
    
    names(auroc_res) <- rownames(study_tab_norm)
    
    return(auroc_res)
}
```

## Test above functions
```{r}
### dataset where we expect 0.5 AUROC

#all data is not-significant
rep_data_p <- rep(.1, 100)
rep_data_p_all <- rep(0.01, 100)

Test_data_p <- data.frame(tool1=rep_data_p,
                                  tool2=rep_data_p,
                                  tool3=rep_data_p)

Test_data_p_all <- data.frame(tool1=rep_data_p_all,
                              tool2=rep_data_p_all,
                              tool3=rep_data_p_all)
# assign rownames (which are ASV names)
rownames(Test_data_p_all) <- paste0("ASV", seq(1,100))


test_data_abundance <- data.frame(matrix(1, 100, 100))
rownames(test_data_abundance) <- paste0("ASV", seq(1,100))
colnames(test_data_abundance) <- paste0("Sample", seq(1,100))

test_data_abundance_1 <- data.frame(matrix(5, 100, 50))
test_data_abundance_2 <- data.frame(matrix(seq(1,100), 100, 50))

test_data_abundance_change <- cbind(test_data_abundance_1,
                                    test_data_abundance_2)

rownames(test_data_abundance_change) <- paste0("ASV", seq(1,100))
colnames(test_data_abundance_change) <- paste0("Sample", seq(1,100))
## make metadata that is clean
rep_gp1 <- rep("case", 50)
rep_gp2 <- rep("control", 50)

test_meta <- data.frame(Comp=c(rep_gp1, rep_gp2))
rownames(test_meta) <- paste0("Sample", seq(1,100))

## test with input of no significant features.
test_no_res <- get_discrim(p_tab = Test_data_p, study_tab = test_data_abundance, meta = test_meta, norm_type = "R.A")

## with all significant features but all have equal abundances
test_res_bad <- get_discrim(p_tab = Test_data_p_all, study_tab = test_data_abundance, meta=test_meta)
test_res_bad
## good all AUROCs return as 0.5 (:

## test using CLR
test_res_bad_CLR <- get_discrim(p_tab = Test_data_p_all, study_tab = test_data_abundance, meta=test_meta, norm_type = "CLR")
test_res_bad_CLR
## good works well!

## works as expected.
test_res_change <- get_discrim(p_tab = Test_data_p_all, study_tab = test_data_abundance_change, meta=test_meta)
test_res_change

test_res_change_CLR <- get_discrim(p_tab = Test_data_p_all, study_tab = test_data_abundance_change, meta=test_meta, norm_type = "CLR")
test_res_change_CLR

#works get
get_AUROC_all_feats(study_tab = test_data_abundance_change, meta = test_meta)


```
## Calculate AUROC of all feats
```{r}
cl <- makeCluster(38)
registerDoParallel(cl)

filt_AUROC_all <- foreach(i=1:length(filt_study_tab[[2]])) %dopar% {
  get_AUROC_all_feats(filt_study_tab[[2]][[i]], meta = metadata[[i]])
}
stopCluster(cl)

length(which(filt_AUROC_all[[1]] > 0.7))

### try unfilt although I do not think this will go very well
cl <- makeCluster(38)
registerDoParallel(cl)

unfilt_AUROC_all <- foreach(i=1:length(unfilt_study_tab[[2]])) %dopar% {
  get_AUROC_all_feats(unfilt_study_tab[[2]][[i]], meta = metadata[[i]])
}
stopCluster(cl)
saveRDS(filt_AUROC_all, "~/GitHub_Repos/Clean_Hackathon/Data/filt_AUROC_all.RDS")
saveRDS(unfilt_AUROC_all, "~/GitHub_Repos/Clean_Hackathon/Data/unfilt_AUROC_all.RDS")

### CLR Values

cl <- makeCluster(38)
registerDoParallel(cl)

filt_AUROC_all_clr <- foreach(i=1:length(filt_study_tab[[2]])) %dopar% {
  get_AUROC_all_feats(filt_study_tab[[2]][[i]], meta = metadata[[i]], norm_type = "CLR")
}
stopCluster(cl)


cl <- makeCluster(38)
registerDoParallel(cl)

unfilt_AUROC_all_clr <- foreach(i=1:length(filt_study_tab[[2]])) %dopar% {
  get_AUROC_all_feats(unfilt_study_tab[[2]][[i]], meta = metadata[[i]], norm_type = "CLR")
}


saveRDS(filt_AUROC_all_clr, "~/GitHub_Repos/Clean_Hackathon/Data/filt_AUROC_all_CLR.RDS")
saveRDS(unfilt_AUROC_all_clr, "~/GitHub_Repos/Clean_Hackathon/Data/unfilt_AUROC_All_CLR.RDS")

```

## Generate AUROC for R.A. data
```{r}
AUROC_R.A_res <- list()

for(i in names(filt_results)){
  AUROC_R.A_res[[i]] <- get_discrim(filt_results[[i]][[2]], study_tab = filt_study_tab[[2]][[i]],
                                         metadata[[i]], norm_type = "R.A")
  
}
saveRDS(AUROC_R.A_res, "~/GitHub_Repos/Clean_Hackathon/Data/AUROC_RA_res.RDS")


## unfilt

AUROC_R.A_res_unfilt <- list()

for(i in names(unfilt_results)){
  AUROC_R.A_res_unfilt[[i]] <- get_discrim(unfilt_results[[i]][[2]], study_tab = unfilt_study_tab[[2]][[i]],
                                      metadata[[i]], norm_type = "R.A")
  
}


saveRDS(AUROC_R.A_res_unfilt, "~/GitHub_Repos/Clean_Hackathon/Data/AUROC_RA_unfilt_res.RDS")
```

## Generate AUROC for CLR data
```{r}
AUROC_CLR_res <- list()


for(i in names(filt_results)){
  AUROC_CLR_res[[i]] <- get_discrim(filt_results[[i]][[2]], study_tab = filt_study_tab[[2]][[i]],
                                         metadata[[i]], norm_type = "CLR")
  
}
saveRDS(AUROC_CLR_res, "~/GitHub_Repos/Clean_Hackathon/Data/AUROC_CLR_res.RDS")



AUROC_CLR_unfilt_res <- list()


for(i in names(unfilt_results)){
  AUROC_CLR_unfilt_res[[i]] <- get_discrim(unfilt_results[[i]][[2]], study_tab = unfilt_study_tab[[2]][[i]],
                                           metadata[[i]], norm_type = "CLR")
  
}

saveRDS(AUROC_CLR_unfilt_res, "~/GitHub_Repos/Clean_Hackathon/Data/AUROC_CLR_unfilt_res.RDS")

```


# Plotting/Analysis

## heatmap generation 
### Filt
#### RA heatmap
Heat map will be of mean of the AUROC of the significant hits identified by each tool.
```{r}
# Load in data and calucalute the means
mean_AUROC_RA <- list()
AUROC_R.A_res <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/AUROC_RA_res.RDS")

for(i in 1:length(AUROC_R.A_res)){
    mean_vals <- vector()
    # get mean for each tool and put it into vector.
    for(j in 1:length(AUROC_R.A_res[[i]])){
      val <- mean(AUROC_R.A_res[[i]][[j]])
      mean_vals <- c(mean_vals, val)
    }
    mean_AUROC_RA[[i]] <- mean_vals
}

#This represents the mean for the first dataset (ArticFreshWaters)
mean_AUROC_RA[[1]]

#Turn the list into a dataframe
mean_AUROC_RA_df <- do.call(rbind, mean_AUROC_RA)

#Assign the proper tool names
colnames(mean_AUROC_RA_df) <- c("ALDEx2", "ANCOM-II", "corncob", "DESeq2", "edgeR", "LEfSe", "MaAsLin2", "MaAsLin2 (rare)", 
                                 "metagenomeSeq", "t-test (rare)", "Wilcoxon (CLR)", "Wilcoxon (rare)", "limma voom (TMM)",
                                 "limma voom (TMMwsp)")


#assign dataset names
rownames(mean_AUROC_RA_df) <- names(AUROC_R.A_res)

#flip the dataset
flip_mean_AUROC_RA_df <- data.frame(t(mean_AUROC_RA_df), check.rows = F, check.names = F)

#assign dataset names to their "formal" name presented in the paper
colnames(flip_mean_AUROC_RA_df) <- Data_set_names[colnames(flip_mean_AUROC_RA_df)]
colnames(flip_mean_AUROC_RA_df)


#order the tools by their name
ordered_flip_mean_AUROC_RA_df <- flip_mean_AUROC_RA_df[sort(rownames(flip_mean_AUROC_RA_df)),]

#scale the data by each dataset so that tools with the highest mean AUROC for that dataset have the highest value
scaled_ordered_flip_mean_AUROC_RA_df <- scale(ordered_flip_mean_AUROC_RA_df, center=T, scale=T)




#plot unscaled version (Not shown in paper)
Unscaled_AUROC_RA_heat <- pheatmap(t(ordered_flip_mean_AUROC_RA_df),
                 cluster_cols = F, na_col = "black",
                 main="Raw")

#round raw vales to 2 digits
ordered_flip_mean_AUROC_RA_df <- round(ordered_flip_mean_AUROC_RA_df, digits = 2)
ordered_flip_mean_AUROC_RA_df[is.na(ordered_flip_mean_AUROC_RA_df)] <- "\u0020"

### then another one that is standardized
Scaled_AUROC_RA_heat <- pheatmap(t(scaled_ordered_flip_mean_AUROC_RA_df),
                                 cluster_cols = F, na_col = "grey",
                                 main="Filtered RA. mean AUROC of sig. ASVs",
                                 display_numbers = t(ordered_flip_mean_AUROC_RA_df),
                                 cluster_rows = F,
                                 angle_col = "45")
```

#### heatmap CLR
Now we create the same heatmap but for CLR AUROCs rather than RA.
```{r}
AUROC_CLR_res <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/AUROC_CLR_res.RDS")

mean_AUROC_CLR <- list()

for(i in 1:length(AUROC_CLR_res)){
    mean_vals <- vector()
    # get mean for each tool and put it into vector.
    for(j in 1:length(AUROC_CLR_res[[i]])){
      val <- mean(AUROC_CLR_res[[i]][[j]])
      mean_vals <- c(mean_vals, val)
    }
    mean_AUROC_CLR[[i]] <- mean_vals
}


mean_AUROC_CLR_df <- do.call(rbind, mean_AUROC_CLR)
colnames(mean_AUROC_CLR_df) <- c("ALDEx2", "ANCOM-II", "corncob", "DESeq2", "edgeR", "LEfSe", "MaAsLin2", "MaAsLin2 (rare)", 
                                 "metagenomeSeq", "t-test (rare)", "Wilcoxon (CLR)", "Wilcoxon (rare)", "limma voom (TMM)",
                                 "limma voom (TMMwsp)")

flip_mean_AUROC_CLR_df <- data.frame(t(mean_AUROC_CLR_df))

colnames(flip_mean_AUROC_CLR_df) <- names(AUROC_CLR_res)
colnames(flip_mean_AUROC_CLR_df) <- Data_set_names[colnames(flip_mean_AUROC_CLR_df)]

ordered_flip_mean_AUROC_CLR_df <- flip_mean_AUROC_CLR_df[sort(rownames(flip_mean_AUROC_CLR_df)),]
scaled_ordered_flip_mean_AUROC_CLR_df <- scale(ordered_flip_mean_AUROC_CLR_df, center=T, scale=T)



ordered_flip_mean_AUROC_CLR_df <- round(ordered_flip_mean_AUROC_CLR_df, digits = 2)
ordered_flip_mean_AUROC_CLR_df[is.na(ordered_flip_mean_AUROC_CLR_df)] <- "\u0020"


scaled_CLR_heat <- pheatmap(t(scaled_ordered_flip_mean_AUROC_CLR_df),
                         cluster_col=F, na_col = "grey",
                         display_numbers = t(ordered_flip_mean_AUROC_CLR_df),
                         main="Filtered CLR mean AUROC sig. ASVs",
                         cluster_rows = F,
                         angle_col = "45")
scaled_CLR_heat
```

### UnFilt
Same as above plots but for unfiltered data. Note that this plots are not in the main manuscript but are including in the display items folder for those that were interested in viewing them.
#### RA heatmap

```{r}
mean_AUROC_RA_unfilt <- list()
AUROC_RA_unfilt_res <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/AUROC_RA_unfilt_res.RDS")

for(i in 1:length(AUROC_RA_unfilt_res)){
  mean_vals <- vector()
  
  for(j in 1:length(AUROC_RA_unfilt_res[[i]])){
    
    val <- mean(AUROC_RA_unfilt_res[[i]][[j]])
    mean_vals <- c(mean_vals, val)
  }
  mean_AUROC_RA_unfilt[[i]] <- mean_vals
}

mean_AUROC_RA_unfilt_df <- do.call(rbind, mean_AUROC_RA_unfilt)
colnames(mean_AUROC_RA_unfilt_df) <- c("ALDEx2", "ANCOM-II", "corncob", "DESeq2", "edgeR", "LEfSe", "MaAsLin2", "MaAsLin2 (rare)", 
                                 "metagenomeSeq", "t-test (rare)", "Wilcoxon (CLR)", "Wilcoxon (rare)", "limma voom (TMM)",
                                 "limma voom (TMMwsp)")


rownames(mean_AUROC_RA_unfilt_df) <- names(AUROC_RA_unfilt_res)
flip_mean_AUROC_RA_unfilt_df <- data.frame(t(mean_AUROC_RA_unfilt_df))

colnames(flip_mean_AUROC_RA_unfilt_df) <- Data_set_names[colnames(flip_mean_AUROC_RA_unfilt_df)]
ordered_flip_mean_AUROC_RA_unfilt_df <- flip_mean_AUROC_RA_unfilt_df[sort(rownames(flip_mean_AUROC_RA_unfilt_df)),]
scaled_ordered_flip_mean_AUROC_RA_unfilt_df <- scale(ordered_flip_mean_AUROC_RA_unfilt_df, center=T, scale = T)


Unscaled_unfilt_RA_heat <- pheatmap(t(ordered_flip_mean_AUROC_RA_unfilt_df),
                                    cluster_cols = F, na_col = "black", 
                                    main="Raw Unfilt")


ordered_flip_mean_AUROC_RA_unfilt_df <- round(ordered_flip_mean_AUROC_RA_unfilt_df, digits = 2)
ordered_flip_mean_AUROC_RA_unfilt_df[is.na(ordered_flip_mean_AUROC_RA_unfilt_df)] <- "\u0020"


Scaled_unfilt_RA_heat <- pheatmap(t(scaled_ordered_flip_mean_AUROC_RA_unfilt_df),
                                  cluster_cols = F, na_col = "grey",
                                  main="Unfiltered RA. mean AUROC sig. ASVs",
                                  display_numbers = t(ordered_flip_mean_AUROC_RA_unfilt_df),
                                  cluster_rows = F,
                                  angle_col = "45")

```


#### CLR heatmap

```{r}
mean_AUROC_CLR_unfilt <- list()
AUROC_CLR_unfilt_res <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/AUROC_CLR_unfilt_res.RDS")

for(i in 1:length(AUROC_CLR_unfilt_res)){
  mean_vals <- vector()
  
  for(j in 1:length(AUROC_CLR_unfilt_res[[i]])){
    
    val <- mean(AUROC_CLR_unfilt_res[[i]][[j]])
    mean_vals <- c(mean_vals, val)
  }
  mean_AUROC_CLR_unfilt[[i]] <- mean_vals
}

mean_AUROC_CLR_unfilt_df <- do.call(rbind, mean_AUROC_CLR_unfilt)

colnames(mean_AUROC_CLR_unfilt_df) <- c("ALDEx2", "ANCOM-II", "corncob", "DESeq2", "edgeR", "LEfSe", "MaAsLin2", "MaAsLin2 (rare)", 
                                 "metagenomeSeq", "t-test (rare)", "Wilcoxon (CLR)", "Wilcoxon (rare)", "limma voom (TMM)",
                                 "limma voom (TMMwsp)")


rownames(mean_AUROC_CLR_unfilt_df) <- names(AUROC_CLR_unfilt_res)
flip_mean_AUROC_CLR_unfilt_df <- data.frame(t(mean_AUROC_CLR_unfilt_df))

colnames(flip_mean_AUROC_CLR_unfilt_df) <- Data_set_names[colnames(flip_mean_AUROC_CLR_unfilt_df)]
ordered_flip_mean_AUROC_CLR_unfilt_df <- flip_mean_AUROC_CLR_unfilt_df[sort(rownames(flip_mean_AUROC_CLR_unfilt_df)),]
scaled_ordered_flip_mean_AUROC_CLR_unfilt_df <- scale(ordered_flip_mean_AUROC_CLR_unfilt_df, center=T, scale = T)


Unscaled_unfilt_CLR_heat <- pheatmap(t(ordered_flip_mean_AUROC_CLR_unfilt_df),
                                    cluster_cols = F, na_col = "black", 
                                    main="Raw CLR Unfilt")
## set NAs to be blank
ordered_flip_mean_AUROC_CLR_unfilt_df <- round(ordered_flip_mean_AUROC_CLR_unfilt_df, digits=2)

ordered_flip_mean_AUROC_CLR_unfilt_df[is.na(ordered_flip_mean_AUROC_CLR_unfilt_df)] <- "\u0020" 

Scaled_unfilt_CLR_heat <- pheatmap(t(scaled_ordered_flip_mean_AUROC_CLR_unfilt_df),
                                  cluster_cols = F, na_col = "grey",
                                  main="Unfiltered CLR. mean AUROC sig. ASVs",
                                  display_numbers = t(ordered_flip_mean_AUROC_CLR_unfilt_df),
                                  number_format = "%.2f",
                                  cluster_rows = F,
                                  angle_col = "45")



```

## Final Figure

```{r}
library(cowplot)

Filtered_Fig <- plot_grid(Scaled_AUROC_RA_heat[[4]], scaled_CLR_heat[[4]], labels=c("A", "B"), ncol=1)
Filtered_Fig

ggsave(filename=paste(display_items_out, "Supp_figures", "Supplemental_AUROC_heatmap.pdf", sep="/"),
       plot = Filtered_Fig, width = 9, height=13, units="in", dpi=600)

ggsave(filename=paste(display_items_out, "Supp_figures", "Supplemental_AUROC_heatmap.png", sep="/"),
       plot = Filtered_Fig, width = 9, height=13, units="in", dpi=150)


Unfiltered_Fig <- plot_grid(Scaled_unfilt_RA_heat[[4]], Scaled_unfilt_CLR_heat[[4]], labels=c("A", "B"), ncol=1)
Unfiltered_Fig
```

## Examination of number of features above 0.7 AUROC
## Comparing AUROC and p-value scatter plot

```{r}
filt_AUROC_all <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/filt_AUROC_all.RDS")


filt_results_AUROC <- filt_results

for(i in 1:length(filt_results_AUROC)){
  
  
  filt_results_AUROC[[i]]$adjP_table <- filt_results_AUROC[[i]]$adjP_table[names(filt_AUROC_all[[i]]),]
  
  
  if(!identical(names(filt_AUROC_all[[i]]), rownames(filt_results_AUROC[[i]]$adjP_table))){
    message("error")
    stop()
  }
  
  filt_results_AUROC[[i]]$adjP_table$AUROC <- filt_AUROC_all[[i]]
  filt_results_AUROC[[i]]$adjP_table$dataset <- names(filt_results_AUROC)[i]
}

## now we need to rbind all the adj-pvalue tables together
all_p_vals_AUROC <- list()

for(i in 1:length(filt_results_AUROC)){
  all_p_vals_AUROC[[i]] <- filt_results_AUROC[[i]]$adjP_table
}

all_p_vals_AUROC_df <- do.call(rbind, all_p_vals_AUROC)

plot(all_p_vals_AUROC_df$aldex2, all_p_vals_AUROC_df$AUROC, xlab="ALDEx2 Q-Val", ylab="AUROC of Feature RA")


melt_all_p_vals_AUROC_df <- reshape2::melt(all_p_vals_AUROC_df, id.vars=c("AUROC", "dataset"))

ALDEx2_only <- melt_all_p_vals_AUROC_df[which(melt_all_p_vals_AUROC_df$variable=="aldex2"),]

ALDEx2_plot <- ggplot(melt_all_p_vals_AUROC_df, aes(x=value, y=AUROC)) + geom_point() + theme_bw() + facet_grid(rows=vars(variable)) + 
  theme(strip.background = element_blank(), strip.text.y = element_text(angle=0)) + xlab("Significance cutoff")
ALDEx2_plot
```
## Precision Recall

### Function
```{r}
# get all featurea above 0.7
get_PR_AUROC <- function(p_tab, AUROC_tab, cutoff=0.7){
  
  p_tab_fix <- p_tab
  
  ## 2 represents a significant hit
  p_tab_fix[p_tab_fix < 0.05 ] <- 2
  
  ## anything that is not 2 (sig hit) we set as 0 (i.e. negative result)
  p_tab_fix[p_tab_fix != 2 ] <- 0
  
  # anything taht was 2 (sig hit) we set as 1 (i.e. positive result)
  p_tab_fix[p_tab_fix == 2] <- 1
  
  #set NAs to 0
  p_tab_fix[is.na(p_tab_fix)] <- 0
  
  #list to hold the results
  disc_res <- list()
  
  
  AUROC_tab_fix <- AUROC_tab
  
  AUROC_tab_fix[AUROC_tab_fix >= cutoff] <- 1
  AUROC_tab_fix[AUROC_tab_fix != 1] <- 0
  

  confusion_data <- list()
  for(i in 1:length(colnames(p_tab_fix))){
    reference_data <- factor(ifelse(AUROC_tab_fix== 1 , "hit", "no"), levels=c("hit", "no"))
    test_data <- factor(ifelse(p_tab_fix[,i]==1, "hit", "no"), levels=c("hit", "no"))
    confusion_data[[i]] <- caret::confusionMatrix(test_data, reference_data, positive="hit", mode="prec_recall")
    
  }
  names(confusion_data) <- colnames(p_tab_fix)
  return(confusion_data)
  
}


get_confusion_stats <- function(all_p_res, all_auroc_res, cutoff=0.7){
  
  recall_res <- list()
  Prec_res <- list()
  F1_res <- list()
  for(i in 1:length(all_p_res)){
    confusion_data <- get_PR_AUROC(all_p_res[[i]]$adjP_table, all_auroc_res[[i]], cutoff = cutoff)
    ## this gives matrix for each tool we need to extract the recall from each tool
    tool_recall <- vector()
    Prec_tool <- vector()
    F1_tool <- vector()
    for(j in 1:length(confusion_data)){
      tool_recall <- c(tool_recall, confusion_data[[j]]$byClass[6])
      Prec_tool <- c(Prec_tool, confusion_data[[j]]$byClass[5])
      F1_tool <- c(F1_tool, confusion_data[[j]]$byClass[7])
    }
    names(tool_recall) <- names(confusion_data)
    names(Prec_tool) <- names(confusion_data)
    names(F1_tool) <- names(confusion_data)
    recall_res[[i]] <- tool_recall
    Prec_res[[i]] <- Prec_tool
    F1_res[[i]] <- F1_tool
  }
  names(recall_res) <- names(all_p_res)
  names(Prec_res) <- names(all_p_res)
  names(F1_res) <- names(all_p_res)
  return(list(recall_res, Prec_res, F1_res))
  
  ## now we need to extract recall, precison, and F1
  
  
}

generate_plot_AUROC_plot <- function(all_p_res, all_auroc_res, cutoff=0.7){
  
  final_res <- get_confusion_stats(all_p_res = all_p_res, all_auroc_res = all_auroc_res, cutoff = cutoff)
  
  ### generate DFs
  recall_df <- do.call(rbind, final_res[[1]])
  prec_df <- do.call(rbind, final_res[[2]])
  f1_df <- do.call(rbind, final_res[[3]])
  
  colnames(recall_df) <- tool_names[colnames(recall_df)]
  colnames(prec_df) <- tool_names[colnames(prec_df)]
  colnames(f1_df) <- tool_names[colnames(f1_df)]
  ## melt them
  melt_recall_df <- melt(recall_df)
  melt_prec_df <- melt(prec_df)
  melt_f1_df <- melt(f1_df)
  
  melt_recall_df$type <- "Recall"
  melt_prec_df$type <- "Precision"
  melt_f1_df$type <- "F1 Score"
  
  ## combind
  comb_df <- rbind(melt_recall_df, melt_prec_df)
  comb_df <- rbind(comb_df, melt_f1_df)
  
  comb_plot <- ggplot(comb_df, aes(x=Var2, y=value)) + geom_boxplot() + xlab("Tool") + ylab("") + geom_quasirandom(pch=21) +
    facet_grid(rows=vars(type)) + theme_bw() + theme(plot.title = element_text(hjust=0.5))
}
```

### Data Analysis
```{r}
filt_AUROC_all <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/filt_AUROC_all.RDS")
unfilt_AUROC_all <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/unfilt_AUROC_all.RDS")
filt_AUROC_all_clr <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/filt_AUROC_all_CLR.RDS")
unfilt_AUROC_all_clr <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/unfilt_AUROC_All_CLR.RDS")




plot_07 <- generate_plot_AUROC_plot(filt_results, filt_AUROC_all, cutoff=0.7) + ggtitle("RA. 0.7 AUROC") + theme(axis.text.x = element_text(angle=35, vjust=.65),
                                                                                                                 axis.title.x = element_blank())
plot_07

means_07_filt <- aggregate(plot_07$data$value, by=list(plot_07$data$Var2, plot_07$data$type), FUN=function(x) median(x, na.rm=T))
View(means_07_filt)

plot_09 <- generate_plot_AUROC_plot(filt_results, filt_AUROC_all, cutoff=0.9) + ggtitle("RA. 0.9 AUROC") + theme(axis.text.x = element_text(angle=35, vjust=.65))
plot_09


means_09_filt <- aggregate(plot_09$data$value, by=list(plot_09$data$Var2, plot_09$data$type), FUN=function(x) median(x, na.rm=T))
View(means_09_filt)


filt_RA <- plot_grid(plot_07, plot_09, ncol=1)

plot_07_unfilt_RA <- generate_plot_AUROC_plot(unfilt_results, unfilt_AUROC_all) + ggtitle("RA. 0.7 AUROC")


plot_09_unfilt_RA <- generate_plot_AUROC_plot(unfilt_results, unfilt_AUROC_all, cutoff=0.9) + ggtitle("RA. 0.9 AUROC")

unfilt_RA <- plot_grid(plot_07_unfilt_RA, plot_09_unfilt_RA, ncol=1)


plot_07_CLR <- generate_plot_AUROC_plot(filt_results, filt_AUROC_all_clr, cutoff=0.7) + ggtitle("CLR. 0.7 AUROC") + theme(axis.text.x = element_text(angle=35, vjust=.65), axis.title.x = element_blank())

plot_07_CLR
plot_07_CLR_data <- aggregate(plot_07_CLR$data$value, by=list(plot_07_CLR$data$Var2, plot_07_CLR$data$type), FUN=function(x) median(x, na.rm=T))


plot_09_CLR <- generate_plot_AUROC_plot(filt_results, filt_AUROC_all_clr, cutoff=0.9) + ggtitle("CLR. 0.9 AUROC") + theme(axis.text.x = element_text(angle=35, vjust=.65))

plot_09_CLR
filt_CLR <- plot_grid(plot_07_CLR, plot_09_CLR, ncol=1)

plot_09_CLR_data <- aggregate(plot_09_CLR$data$value, by=list(plot_09_CLR$data$Var2, plot_09_CLR$data$type), FUN=function(x) median(x, na.rm=T))

plot_07_unfilt_CLR <- generate_plot_AUROC_plot(unfilt_results, unfilt_AUROC_all_clr, cutoff = 0.7) + ggtitle("AUROC Cutoff 0.7")
plot_09_unfilt_CLR <- generate_plot_AUROC_plot(unfilt_results, unfilt_AUROC_all_clr, cutoff = 0.9) + ggtitle("AUROC Cutoff 0.9")

unfilt_CLR <- plot_grid(plot_07_unfilt_CLR, plot_09_unfilt_CLR, ncol=1)


final_sup_fig <-plot_grid(filt_RA, filt_CLR, labels=c("A", "B"))
final_sup_fig
```

### Final Figure Generation
```{r}
final_sup_fig <-plot_grid(filt_RA, filt_CLR)
final_sup_fig

ggsave(filename=paste(display_items_out, "Supp_figures", "Supplemental_AUROC_F1.pdf", sep="/"),
       plot = final_sup_fig, width = 9, height=13, units="in", dpi=600)

ggsave(filename=paste(display_items_out, "Supp_figures", "Supplemental_AUROC_F1.png", sep="/"),
       plot = final_sup_fig, width = 9, height=13, units="in", dpi=150)
```