---
title: "Discriminatory Analysis"
author: "Jacob T. Nearing"
date: "7/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("/home/jacob/projects/HACKATHON_ANCOM_FIX_21_03_13/Hackathon/Studies/")


display_items_out <- "/home/jacob/GitHub_Repos/Clean_Hackathon/Display_items/"

library(ROCR)
library(pheatmap)
library(foreach)
library(doParallel)
library(ggplot2)
library(reshape2)
library(cowplot)
library(dplyr)


library(RColorBrewer)
library(ggbeeswarm)
n <- 38
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))

Data_set_names <- c(ArcticFireSoils="Soil - Fires",
                         ArcticFreshwaters="Freshwater - Arctic",
                         ArcticTransects="Soil - Arctic",
                         art_scher="Human - RA",
                         asd_son= "Human - ASD",
                         BISCUIT= "Human - CD (1)",
                         Blueberry= "Soil - Blueberry",
                         cdi_schubert="Human - C. diff (1)",
                         cdi_vincent="Human - C. diff (2)",
                         Chemerin="Mouse Facilities",
                         crc_baxter="Human - CC (1)",
                         crc_zeller="Human - CC (2)",
                         edd_singh="Human - Inf.",
                         Exercise="Mouse - Exercised",
                         glass_plastic_oberbeckmann="Marine - Plastic (4)",
                         GWMC_ASIA_NA="WWSR - Continents",
                         GWMC_HOT_COLD="WWSR - Temp.",
                         hiv_dinh="Human - HIV (1)",
                         hiv_lozupone="Human - HIV (2)",
                         hiv_noguerajulian="Human - HIV (3)",
                         ibd_gevers="Human - CD (2)",
                         ibd_papa="Human - IBD",
                         Ji_WTP_DS="Freshwater - Treat.",
                         MALL="Human - ALL",
                         ob_goodrich="Human - OB (1)",
                         ob_ross="Human - OB (2)",
                         ob_turnbaugh="Human - OB (3)",
                         ob_zhu="Human - OB (4)",
                         ###"ob_zupancic",
                         Office="Built - Office",
                         par_scheperjans="Human - Par.",
                         sed_plastic_hoellein="Marine - Plastic (2)",
                         sed_plastic_rosato="Marine - Plastic (5)",
                         seston_plastic_mccormick="River - Plastic",
                         sw_plastic_frere="Marine - Plastic (1)",
                         sw_sed_detender="Marine - Sediment",
                          t1d_alkanani="Human - T1D (1)",
                         t1d_mejialeon="Human - T1D (2)",
                         wood_plastic_kesy="Marine - Plastic (3)")

tool_names <- c(aldex2="ALDEx2", ancom="ANCOM-II", corncob="corncob", deseq2="DESeq2", edger="edgeR", lefse="LEfSe", 
                limma_voom_TMM="limma voom (TMM)", limma_voom_TMMwsp="limma voom (TMMwsp)", maaslin2="MaAsLin2",
                maaslin2rare="MaAsLin2 (rare)", metagenomeSeq="metagenomeSeq", ttestrare="t-test (rare)", 
                wilcoxonclr="Wilcoxon (CLR)", wilcoxonrare="Wilcoxon (rare)")


## function to read in all the metadata files
read_metadata <- function(study_list){
  ret_meta <- list()
  
  for(i in 1:length(study_list)){
    
    meta_file <- list.files(study_list[i], pattern="*_meta*")
    meta_file_name <- paste(study_list[i], meta_file, sep="/")
    message(meta_file_name)
    ret_meta[[study_list[i]]] <- read.table(meta_file_name, header=T, sep="\t", comment.char="", quote="", check.names = F, row.names = 1)
  }
  return(ret_meta)
}
```

## load in data

```{r}
filt_results <- readRDS("/home/jacob/GitHub_Repos/Hackathon_testing/Data/Filt_results_21_04_07.RDS")
unfilt_results <- readRDS("/home/jacob/GitHub_Repos/Hackathon_testing/Data/Unfilt_results_21_04_07.RDS")

unfilt_study_tab  <- readRDS("/home/jacob/GitHub_Repos/Hackathon_testing/Data/unfilt_study_tab_21_04_07.RDS")
filt_study_tab <- readRDS("/home/jacob/GitHub_Repos/Hackathon_testing/Data/filt_study_tab_21_04_07.RDS")

## load in data classes
hackathon_study_ids <- c("ArcticFireSoils",
                         "ArcticFreshwaters",
                         "ArcticTransects",
                         "art_scher",
                         "asd_son",
                         "BISCUIT",
                         "Blueberry",
                         "cdi_schubert",
                         "cdi_vincent",
                         "Chemerin",
                         "crc_baxter",
                         "crc_zeller",
                         "edd_singh",
                         "Exercise",
                         "glass_plastic_oberbeckmann",
                         "GWMC_ASIA_NA",
                         "GWMC_HOT_COLD",
                         "hiv_dinh",
                         "hiv_lozupone",
                         "hiv_noguerajulian",
                         "ibd_gevers",
                         "ibd_papa",
                         "Ji_WTP_DS",
                         "MALL",
                         "ob_goodrich",
                         "ob_ross",
                         "ob_turnbaugh",
                         "ob_zhu",
                         ###"ob_zupancic",
                         "Office",
                         "par_scheperjans",
                         "sed_plastic_hoellein",
                         "sed_plastic_rosato",
                         "seston_plastic_mccormick",
                         "sw_plastic_frere",
                         "sw_sed_detender",
                          "t1d_alkanani",
                         "t1d_mejialeon",
                         "wood_plastic_kesy")


metadata <- read_metadata(hackathon_study_ids)
```

# Data generation
## Function

```{r}

##Function takes in p_table and list of AUROC of features that are contained within that table..
## it then returns a list containing the AUROC of all features that were found to be significant for each tool...

get_sig_AUROC <- function(p_tab, AUROC_vec){
  
  ret_list <- list()
  sig_feats <- vector()
  
  #make sure they are the same dims
  
  #make sure they are the same length
  stopifnot(nrow(p_tab) == length(AUROC_vec))
  
  for(tool in colnames(p_tab)){
    sig_feats <- rownames(p_tab)[which(p_tab[,tool] < 0.05)]
    
    ret_list[[tool]] <- AUROC_vec[sig_feats]
    
  }

  return(ret_list)
}


#this function will calculate the AUROC of all features in a dataset depending on the normalization type.
get_AUROC_all_feats <- function(study_tab, meta, norm_type="R.A"){
   
    ## Normalize table
   if(norm_type=="R.A"){
          study_tab_norm <- sweep(study_tab, 2, colSums(study_tab), '/')
    }else if(norm_type=="CLR"){
      study_tab_norm <- data.frame(apply(study_tab + 1, 2, function(x) {log(x) - mean (log(x))} ), check.names = F)
    }else{
      message("Please pick a normalization method")
      stop()
    }
  
    ## make sure metadata and study table have same samples
    if(!identical(colnames(study_tab_norm), rownames(meta))){
      rows_to_keep <- intersect(colnames(study_tab_norm), rownames(meta))
      meta <- meta[rows_to_keep,,drop=F]
      study_tab_norm <- study_tab_norm[,rows_to_keep]
    }
    auroc_res <- vector()
    for(i in 1:length(rownames(study_tab_norm))){
      test_data <- as.numeric(study_tab_norm[i,])
      ### one issue is that the prediction assumes that a higher number is indicative of the second class
      ### this is obviously not what we want in this analysis as the microbe could be up or down in either class
      ### we will need to fix this when calculating the auroc performance
      ### as such we will subtract the result from 0.5 and take the abs and than add 0.5 back. 
      ### this will give us classification performance in either direction.
      test_pred <- ROCR::prediction(predictions = test_data, labels = meta[,1])
      test_perf <- ROCR::performance(test_pred, measure="auc")
      test_result <- abs(0.5 - as.numeric(test_perf@y.values[1])) + 0.5
      auroc_res <- c(auroc_res, test_result)
      
    }
    
    names(auroc_res) <- rownames(study_tab_norm)
    
    return(auroc_res)
}
```

## Test above functions
```{r, eval=F}
### dataset where we expect 0.5 AUROC

#all data is not-significant
rep_data_p <- rep(.1, 100)
rep_data_p_all <- rep(0.01, 100)

Test_data_p <- data.frame(tool1=rep_data_p,
                                  tool2=rep_data_p,
                                  tool3=rep_data_p)

Test_data_p_all <- data.frame(tool1=rep_data_p_all,
                              tool2=rep_data_p_all,
                              tool3=rep_data_p_all)
# assign rownames (which are ASV names)
rownames(Test_data_p_all) <- paste0("ASV", seq(1,100))


test_data_abundance <- data.frame(matrix(1, 100, 100))
rownames(test_data_abundance) <- paste0("ASV", seq(1,100))
colnames(test_data_abundance) <- paste0("Sample", seq(1,100))

test_data_abundance_1 <- data.frame(matrix(5, 100, 50))
test_data_abundance_2 <- data.frame(matrix(seq(1,100), 100, 50))

test_data_abundance_change <- cbind(test_data_abundance_1,
                                    test_data_abundance_2)

rownames(test_data_abundance_change) <- paste0("ASV", seq(1,100))
colnames(test_data_abundance_change) <- paste0("Sample", seq(1,100))
## make metadata that is clean
rep_gp1 <- rep("case", 50)
rep_gp2 <- rep("control", 50)

test_meta <- data.frame(Comp=c(rep_gp1, rep_gp2))
rownames(test_meta) <- paste0("Sample", seq(1,100))


#works get
get_AUROC_all_feats(study_tab = test_data_abundance_change, meta = test_meta)






test_meta2 <- data.frame(Comp=c(rep(c("case","control"), 50)))
rownames(test_meta2) <- paste0("Sample", seq(1,100))

get_AUROC_all_feats(study_tab = test_data_abundance_change, meta=test_meta2)

test_data_abundance_change$Sample100 <- 10
test_data_abundance_change$Sample99 <- 98
test_data_abundance_change$Sample98 <- 100

get_AUROC_all_feats(study_tab = test_data_abundance_change, meta = test_meta)
```
## Calculate AUROC of all feats
```{r, eval=F}
cl <- makeCluster(38)
registerDoParallel(cl)

filt_AUROC_all <- foreach(i=1:length(filt_study_tab[[2]])) %dopar% {
  get_AUROC_all_feats(filt_study_tab[[2]][[i]], meta = metadata[[i]])
}
stopCluster(cl)

length(which(filt_AUROC_all[[1]] > 0.7))

### try unfilt although I do not think this will go very well
cl <- makeCluster(38)
registerDoParallel(cl)

unfilt_AUROC_all <- foreach(i=1:length(unfilt_study_tab[[2]])) %dopar% {
  get_AUROC_all_feats(unfilt_study_tab[[2]][[i]], meta = metadata[[i]])
}
stopCluster(cl)
saveRDS(filt_AUROC_all, "~/GitHub_Repos/Clean_Hackathon/Data/filt_AUROC_all.RDS")
saveRDS(unfilt_AUROC_all, "~/GitHub_Repos/Clean_Hackathon/Data/unfilt_AUROC_all.RDS")

### CLR Values

cl <- makeCluster(38)
registerDoParallel(cl)

filt_AUROC_all_clr <- foreach(i=1:length(filt_study_tab[[2]])) %dopar% {
  get_AUROC_all_feats(filt_study_tab[[2]][[i]], meta = metadata[[i]], norm_type = "CLR")
}
stopCluster(cl)


cl <- makeCluster(38)
registerDoParallel(cl)

unfilt_AUROC_all_clr <- foreach(i=1:length(filt_study_tab[[2]])) %dopar% {
  get_AUROC_all_feats(unfilt_study_tab[[2]][[i]], meta = metadata[[i]], norm_type = "CLR")
}


saveRDS(filt_AUROC_all_clr, "~/GitHub_Repos/Clean_Hackathon/Data/filt_AUROC_all_CLR.RDS")
saveRDS(unfilt_AUROC_all_clr, "~/GitHub_Repos/Clean_Hackathon/Data/unfilt_AUROC_All_CLR.RDS")

```


# Plotting/Analysis

## heatmap generation 

Function for generating heatmaps
```{r}

get_median_heat <- function(p_list, AUROC_list, dataset_names, tool_rename, main="", return_data=FALSE){
  
  sig_AUROCs <- list()
  for(i in 1:length(AUROC_list)){
    sig_AUROCs[[i]] <- get_sig_AUROC(p_list[[i]][[2]], AUROC_list[[i]])
  }
  
  median_vals <- matrix(-1, nrow=38, ncol=14)
  colnames(median_vals) <- names(sig_AUROCs[[1]])
  rownames(median_vals) <- names(p_list)
  
  #caluclate medians
  for(i in 1:length(sig_AUROCs)){
    for(tool in names(sig_AUROCs[[i]])){
      median_vals[i, tool] <- median(sig_AUROCs[[i]][[tool]], na.rm = T)
    }
  }
  rownames(median_vals) <- dataset_names[rownames(median_vals)]
  colnames(median_vals) <- tool_rename[colnames(median_vals)]

  flip_median_vals <- t(median_vals)

  #order the tools by name
  ordered_flip_median_vals <- flip_median_vals[sort(rownames(flip_median_vals)),]
  
  #scale them so they can be compared across rows in the heatmap
  scaled_orded_flip_median_vals <- scale(ordered_flip_median_vals, center=T, scale=T)

  #round to 2 digits
  ordered_flip_median_vals <- round(ordered_flip_median_vals, digits = 2)
  
  if(return_data){
    return(ordered_flip_median_vals)  
  }
  #add blank character for NA values
  ordered_flip_median_vals[is.na(ordered_flip_median_vals)] <- "\u0020"


  #flip matrix so rows are datasets and columns are tools
  Scaled_heatmap <- pheatmap(t(scaled_orded_flip_median_vals),
                                cluster_cols = F, 
                                na_col="grey",
                                main=main,
                                display_numbers = t(ordered_flip_median_vals),
                                cluster_rows = F,
                                angle_col = "45")
  #return heatmap
  return(Scaled_heatmap)
}

```

### Filt
#### RA heatmap

Heatmap of mean AUROC of the significant hits identified by each tool (perhaps I want to use median here....)
```{r}
AUROC_FILT_all_RA <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/filt_AUROC_all.RDS")


Scaled_filt_heatmap_RA <- get_median_heat(filt_results, AUROC_FILT_all_RA, dataset_names = Data_set_names, tool_rename = tool_names,
                                          main="Filtered RA. median AUROC sig. ASVs")


filt_heat_data <- get_median_heat(filt_results, AUROC_FILT_all_RA, dataset_names = Data_set_names, tool_rename = tool_names,
                                          main="Filtered RA. median AUROC sig. ASVs", return_data = T)
write.table(x=filt_heat_data, file="~/GitHub_Repos/Clean_Hackathon/Plotting_data/Supp_figures/Supp_Fig3A.csv", col.names = NA,
            row.names = T, quote=F, sep=",")
```

#### heatmap CLR
Now we create the same heatmap but for CLR AUROCs rather than RA.
```{r}
AUROC_FILT_all_CLR <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/filt_AUROC_all_CLR.RDS")

Scaled_filt_heatmap_CLR <- get_median_heat(filt_results, AUROC_FILT_all_CLR, dataset_names = Data_set_names, tool_rename = tool_names,
                                           main="Filtered CLR median AUROC sig. ASVs")

filt_heat_data_CLR <- get_median_heat(filt_results, AUROC_FILT_all_CLR, dataset_names = Data_set_names, tool_rename = tool_names,
                                           main="Filtered CLR median AUROC sig. ASVs", return_data = T)

write.table(x=filt_heat_data_CLR, file="~/GitHub_Repos/Clean_Hackathon/Plotting_data/Supp_figures/Supp_Fig3B.csv", col.names = NA,
            row.names = T, quote=F, sep=",")
```

### UnFilt
Same as above plots but for unfiltered data. Note that this plots are not in the main manuscript but are including in the display items folder for those that were interested in viewing them.
#### RA heatmap

```{r}
AUROC_unFILT_all_RA <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/unfilt_AUROC_all.RDS")

Scaled_unfilt_heatmap_RA <- get_median_heat(unfilt_results, AUROC_unFILT_all_RA, dataset_names = Data_set_names, tool_rename = tool_names,
                                            main="Unfiltered RA. median AUROC sig. ASVs")

```


#### CLR heatmap

```{r}
AUROC_unFILT_all_CLR <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/unfilt_AUROC_All_CLR.RDS")


Scaled_unfilt_heatmap_CLR <- get_median_heat(unfilt_results, AUROC_unFILT_all_CLR, dataset_names = Data_set_names, tool_rename = tool_names,
                                             main="Unfiltered CLR. median AUROC sig. ASVs")

```

## Final Figure

```{r}
library(cowplot)

Filtered_Fig <- plot_grid(Scaled_filt_heatmap_RA[[4]], Scaled_filt_heatmap_CLR[[4]], labels=c("A", "B"), ncol=1)
Filtered_Fig

ggsave(filename=paste(display_items_out, "Supp_figures", "Supplemental_AUROC_heatmap.pdf", sep="/"),
       plot = Filtered_Fig, width = 9, height=13, units="in", dpi=600)

ggsave(filename=paste(display_items_out, "Supp_figures", "Supplemental_AUROC_heatmap.png", sep="/"),
       plot = Filtered_Fig, width = 9, height=13, units="in", dpi=150)


Unfiltered_Fig <- plot_grid(Scaled_unfilt_heatmap_RA[[4]], Scaled_unfilt_heatmap_CLR[[4]], labels=c("A", "B"), ncol=1)
Unfiltered_Fig

ggsave(filename=paste(display_items_out, "Supp_figures", "AUROC_heatmap_UNFILT.pdf", sep="/"),
       plot = Unfiltered_Fig, width = 9, height=13, units="in", dpi=600)

ggsave(filename=paste(display_items_out, "Supp_figures", "AUROC_heatmap_UNFILT.png", sep="/"),
       plot = Unfiltered_Fig, width = 9, height=13, units="in", dpi=150)

```


## Precision Recall of ASVs above X AUROC for each tool

### Function
```{r}
# get all featurea above 0.7
get_PR_AUROC <- function(p_tab, AUROC_tab, cutoff=0.7){
  
  p_tab_fix <- p_tab
  
  ## 2 represents a significant hit
  p_tab_fix[p_tab_fix < 0.05 ] <- 2
  
  ## anything that is not 2 (sig hit) we set as 0 (i.e. negative result)
  p_tab_fix[p_tab_fix != 2 ] <- 0
  
  # anything taht was 2 (sig hit) we set as 1 (i.e. positive result)
  p_tab_fix[p_tab_fix == 2] <- 1
  
  #set NAs to 0
  p_tab_fix[is.na(p_tab_fix)] <- 0
  
  #list to hold the results
  disc_res <- list()
  
  
  AUROC_tab_fix <- AUROC_tab
  
  AUROC_tab_fix[AUROC_tab_fix >= cutoff] <- 10
  AUROC_tab_fix[AUROC_tab_fix != 10] <- 0
  

  confusion_data <- list()
  for(i in 1:length(colnames(p_tab_fix))){
    reference_data <- factor(ifelse(AUROC_tab_fix== 10 , "hit", "no"), levels=c("hit", "no"))
    test_data <- factor(ifelse(p_tab_fix[,i]==1, "hit", "no"), levels=c("hit", "no"))
    confusion_data[[i]] <- caret::confusionMatrix(test_data, reference_data, positive="hit", mode="prec_recall")
    
  }
  names(confusion_data) <- colnames(p_tab_fix)
  return(confusion_data)
  
}


get_confusion_stats <- function(all_p_res, all_auroc_res, cutoff=0.7){
  
  recall_res <- list()
  Prec_res <- list()
  F1_res <- list()
  for(i in 1:length(all_p_res)){
    confusion_data <- get_PR_AUROC(all_p_res[[i]]$adjP_table, all_auroc_res[[i]], cutoff = cutoff)
    ## this gives matrix for each tool we need to extract the recall from each tool
    tool_recall <- vector()
    Prec_tool <- vector()
    F1_tool <- vector()
    for(j in 1:length(confusion_data)){
      tool_recall <- c(tool_recall, confusion_data[[j]]$byClass[6])
      Prec_tool <- c(Prec_tool, confusion_data[[j]]$byClass[5])
      F1_tool <- c(F1_tool, confusion_data[[j]]$byClass[7])
    }
    names(tool_recall) <- names(confusion_data)
    names(Prec_tool) <- names(confusion_data)
    names(F1_tool) <- names(confusion_data)
    recall_res[[i]] <- tool_recall
    Prec_res[[i]] <- Prec_tool
    F1_res[[i]] <- F1_tool
  }
  names(recall_res) <- names(all_p_res)
  names(Prec_res) <- names(all_p_res)
  names(F1_res) <- names(all_p_res)
  return(list(recall_res, Prec_res, F1_res))
  
  ## now we need to extract recall, precison, and F1
  
  
}

generate_plot_AUROC_plot <- function(all_p_res, all_auroc_res, cutoff=0.7){
  
  final_res <- get_confusion_stats(all_p_res = all_p_res, all_auroc_res = all_auroc_res, cutoff = cutoff)
  
  ### generate DFs
  recall_df <- do.call(rbind, final_res[[1]])
  prec_df <- do.call(rbind, final_res[[2]])
  f1_df <- do.call(rbind, final_res[[3]])
  
  colnames(recall_df) <- tool_names[colnames(recall_df)]
  colnames(prec_df) <- tool_names[colnames(prec_df)]
  colnames(f1_df) <- tool_names[colnames(f1_df)]
  ## melt them
  melt_recall_df <- melt(recall_df)
  melt_prec_df <- melt(prec_df)
  melt_f1_df <- melt(f1_df)
  
  melt_recall_df$type <- "Recall"
  melt_prec_df$type <- "Precision"
  melt_f1_df$type <- "F1 Score"
  
  ## combind
  comb_df <- rbind(melt_recall_df, melt_prec_df)
  comb_df <- rbind(comb_df, melt_f1_df)
  
  #remove rows that are NA as they provide no information
  comb_df <- na.omit(comb_df)

  comb_plot <- ggplot(comb_df, aes(x=Var2, y=value)) + geom_boxplot() + xlab("Tool") + ylab("") + geom_quasirandom(pch=21, groupOnX = T) +
    facet_grid(rows=vars(type)) + theme_bw() + theme(plot.title = element_text(hjust=0.5))
}
```

## Test above functions
```{r}
test_all_aurocs <- c(1:100/100)
test_all_aurocs

rep_data_p <- rep(.1, 100)
rep_data_p_all <- rep(0.01, 100)
rep_data_p_alt <- rep(c(.1, 0.01), 50)

Test_data_p <- data.frame(aldex2=rep_data_p,
                                  ancom=rep_data_p,
                                  corncob=rep_data_p)

Test_data_p_all <- data.frame(aldex2=rep_data_p_all,
                              ancom=rep_data_p_all,
                              corncob=rep_data_p_all)

Test_data_p_alt <- data.frame(aldex2=rep_data_p_alt,
                              ancom=rep_data_p_alt,
                              corncob=rep_data_p_alt)

# assign rownames (which are ASV names)
rownames(Test_data_p_all) <- paste0("ASV", seq(1,100))

test_all_p <- list("rawr"=Test_data_p_all, 'adjP_table'=Test_data_p_all)
test_no_p <- list("rawr"=Test_data_p, 'adjP_table'=Test_data_p)
test_alt_p <- list("rawr"=Test_data_p_alt, 'adjP_table'=Test_data_p_alt)

test_all_p_list <- list(test_all_p, test_no_p, test_alt_p)
test_all_aurocs_list <- list(test_all_aurocs, test_all_aurocs, test_all_aurocs)

#okay that is exactly as I would expect to get
get_PR_AUROC(Test_data_p_all, test_all_aurocs)
#none are significant so recall should be NA and so is prec. 

get_PR_AUROC(Test_data_p, test_all_aurocs)
#when non are significant it says Precision is NA.

get_PR_AUROC(Test_data_p_alt, test_all_aurocs)


test_res <- get_confusion_stats(test_all_p_list, test_all_aurocs_list)
## first thing in list is recall, second is prec, third is f1

test_plot <- generate_plot_AUROC_plot(all_p_res = test_all_p_list, all_auroc_res = test_all_aurocs_list, cutoff = 0.7)
test_plot

# okay that makes sense!

```

### Data Analysis

#### load data
```{r}
filt_AUROC_all <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/filt_AUROC_all.RDS")
unfilt_AUROC_all <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/unfilt_AUROC_all.RDS")
filt_AUROC_all_clr <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/filt_AUROC_all_CLR.RDS")
unfilt_AUROC_all_clr <- readRDS("~/GitHub_Repos/Clean_Hackathon/Data/unfilt_AUROC_All_CLR.RDS")
```

#### 0.7 RA Filt
```{r}
plot_07 <- generate_plot_AUROC_plot(filt_results, filt_AUROC_all, cutoff=0.7) + ggtitle("RA. 0.7 AUROC") + theme(axis.text.x = element_text(angle=35, vjust=.65),
                                                                                                                 axis.title.x = element_blank())

median_07_filt <- aggregate(plot_07$data$value, by=list(plot_07$data$Var2, plot_07$data$type), FUN=function(x) median(x, na.rm=T))
#median precision
dplyr::filter(median_07_filt, Group.2=="Precision") %>% arrange(x)
#median recall
dplyr::filter(median_07_filt, Group.2=="Recall") %>% arrange(x)


SD_07_filt <- aggregate(plot_07$data$value, by=list(plot_07$data$Var2, plot_07$data$type), FUN=function(x) sd(x, na.rm=T))
#sd precision
dplyr::filter(SD_07_filt, Group.2=="Precision") %>% arrange(x)

#write out csv file that contains plotting data
write.table(x=plot_07$data, file="~/GitHub_Repos/Clean_Hackathon/Plotting_data/Supp_figures/Supp_Fig4_RA_07.csv", col.names = NA, 
            row.names = T, quote=F, sep=",")
```

#### 0.9 RA Filt
````{r}
plot_09 <- generate_plot_AUROC_plot(filt_results, filt_AUROC_all, cutoff=0.9) + ggtitle("RA. 0.9 AUROC") + theme(axis.text.x = element_text(angle=35, vjust=.65))



median_09_filt <- aggregate(plot_09$data$value, by=list(plot_09$data$Var2, plot_09$data$type), FUN=function(x) median(x, na.rm=T))
#get median precision
dplyr::filter(median_09_filt, Group.2=="Precision") %>% arrange(x)

#get median recall
dplyr::filter(median_09_filt, Group.2=="Recall") %>% arrange(x)


#write csv used to plot data
write.table(x=plot_09$data, file="~/GitHub_Repos/Clean_Hackathon/Plotting_data/Supp_figures/Supp_Fig4_RA_09.csv", col.names = NA,
            row.names = T, quote=F, sep=",")
#generate RA part of supplemental figure
filt_RA <- plot_grid(plot_07, plot_09, ncol=1)
```

#### 0.7 CLR filt
```{r}
plot_07_CLR <- generate_plot_AUROC_plot(filt_results, filt_AUROC_all_clr, cutoff=0.7) + ggtitle("CLR. 0.7 AUROC") + theme(axis.text.x = element_text(angle=35, vjust=.65), axis.title.x = element_blank())


plot_07_CLR_data <- aggregate(plot_07_CLR$data$value, by=list(plot_07_CLR$data$Var2, plot_07_CLR$data$type), FUN=function(x) median(x, na.rm=T))
#get median precision
dplyr::filter(plot_07_CLR_data, Group.2=="Precision") %>% arrange(x)
#get median recall
dplyr::filter(plot_07_CLR_data, Group.2=="Recall") %>% arrange(x)
#get median F1
dplyr::filter(plot_07_CLR_data, Group.2=="F1 Score") %>% arrange(x)

SD_plot_07_CLR_data <- aggregate(plot_07_CLR$data$value, by=list(plot_07_CLR$data$Var2, plot_07_CLR$data$type), FUN=function(x) sd(x, na.rm=T))
#get SD
dplyr::filter(SD_plot_07_CLR_data, Group.2=="Precision") %>% arrange(x)

#write csv used to plot data
write.table(x=plot_07_CLR$data, file="~/GitHub_Repos/Clean_Hackathon/Plotting_data/Supp_figures/Supp_Fig4_CLR_07.csv",  col.names = NA,
            row.names = T, quote=F, sep=",")
```

#### 0.9 CLR Filt
```{r}
plot_09_CLR <- generate_plot_AUROC_plot(filt_results, filt_AUROC_all_clr, cutoff=0.9) + ggtitle("CLR. 0.9 AUROC") + theme(axis.text.x = element_text(angle=35, vjust=.65))


filt_CLR <- plot_grid(plot_07_CLR, plot_09_CLR, ncol=1)

plot_09_CLR_data <- aggregate(plot_09_CLR$data$value, by=list(plot_09_CLR$data$Var2, plot_09_CLR$data$type), FUN=function(x) median(x, na.rm=T))
#median recall
dplyr::filter(plot_09_CLR_data, Group.2=="Recall") %>% arrange(x)

#median Precision
dplyr::filter(plot_09_CLR_data, Group.2=="Precision") %>% arrange(x)

#write plotting data
write.table(x=plot_09_CLR$data, file="~/GitHub_Repos/Clean_Hackathon/Plotting_data/Supp_figures/Supp_Fig4_CLR_09.csv", col.names = NA,
            row.names = T, quote=F, sep=",")
```

#### Unfilt
These plots were not including in the manuscript due to length resitrictions. That being said they show similar trends as the filtered data. 
##### 0.7 RA UnFilt
````{r}
plot_07_unfilt_RA <- generate_plot_AUROC_plot(unfilt_results, unfilt_AUROC_all) + ggtitle("RA. 0.7 AUROC")
```

##### 0.9 RA UnFilt
```{r}
plot_09_unfilt_RA <- generate_plot_AUROC_plot(unfilt_results, unfilt_AUROC_all, cutoff=0.9) + ggtitle("RA. 0.9 AUROC")

unfilt_RA <- plot_grid(plot_07_unfilt_RA, plot_09_unfilt_RA, ncol=1)
```


##### 0.7 CLR Unfilt
```{r}
plot_07_unfilt_CLR <- generate_plot_AUROC_plot(unfilt_results, unfilt_AUROC_all_clr, cutoff = 0.7) + ggtitle("AUROC Cutoff 0.7")
```

##### 0.9 CLR Unfilt
```{r}
plot_09_unfilt_CLR <- generate_plot_AUROC_plot(unfilt_results, unfilt_AUROC_all_clr, cutoff = 0.9) + ggtitle("AUROC Cutoff 0.9")

unfilt_CLR <- plot_grid(plot_07_unfilt_CLR, plot_09_unfilt_CLR, ncol=1)
```

### Final Figure Generation
```{r}
final_sup_fig <-plot_grid(filt_RA, filt_CLR)
final_sup_fig

ggsave(filename=paste(display_items_out, "Supp_figures", "Supp_Fig4.pdf", sep="/"),
       plot = final_sup_fig, width = 9, height=13, units="in", dpi=600)

ggsave(filename=paste(display_items_out, "Supp_figures", "Supp_Fig4.png", sep="/"),
       plot = final_sup_fig, width = 9, height=13, units="in", dpi=150)

ggsave(filename=paste(display_items_out, "Misc_figures", "Supplemental_AUROC_F1_unfilt.pdf", sep="/"),
       plot = final_sup_fig_unfilt, width = 9, height=13, units="in", dpi=600)

ggsave(filename=paste(display_items_out, "Misc_figures", "Supplemental_AUROC_F1_unfilt.png", sep="/"),
       plot = final_sup_fig_unfilt, width = 9, height=13, units="in", dpi=150)

```